Constraining the Interiors of Asteroids Through Close Encounters

### 2022-06-28 paper/main.tex
Changed example data plot

The observational parameters also impose strict thresholds, most of all the uncertainty of the data set $\sigma_P / P$ and $\sigma_\rho$. Instantaneous rotational period uncertainty of less than one part in one million is required to resolve precise details of the asteroid density distribution. This could be accomplished by multiple, precise period measurements, increasing the time between observations to maximize the change in period between observations, increasing the data set to include more post-flyby tumbling data, or if necessary by increasing precision in the other observational parameters to relieve the burden on asteroid period. The instantaneous spin pole direction of the asteroid must also be known with precision on the order of degrees. However, the cadence of observations and the possibility of missing data points does not strongly affect results. Observations can be as much as 30 minutes apart and as much as 1.5 hr can be left out of the data set (equivalent to 45 missing data points for the reference 2 minute cadence) due to the asteroid passing in front of the sun, for example.

>>>>

The observational parameters also impose strict thresholds, most of all the uncertainty of the data set $\sigma_P / P$ and $\sigma_\rho$. Instantaneous rotational period uncertainty of less than one part in one million is required to resolve precise details of the asteroid density distribution. This could be accomplished by multiple, precise period measurements, increasing the time between observations to maximize the change in period between observations, increasing the data set to include more post-flyby tumbling data, or if necessary by increasing precision in the other observational parameters to relieve the burden on asteroid period. The instantaneous spin pole direction of the asteroid must also be known with precision on the order of degrees. However, the cadence of observations and the possibility of missing data points does not strongly affect results. Observations can be as much as 30 minutes apart and as much as 1.5 hr can be left out of the data set (equivalent to 45 missing data points for the reference 2 minute cadence), even during the high-torque perigee. The latter could be caused by the asteroid passing in front of the sun, for example.
